---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
   warning = FALSE, message = FALSE
)
```

## diseasesdeathrate

<!-- badges: start -->
<!-- badges: end -->

The `diseasesdeathrate` package provides access to age-standardized death rate data for infectious and parasitic diseases across multiple Asian countries. Sourced from the `World Health Organization` (WHO), this package enables users to analyze and visualize health trends related to infectious diseases, providing insights into public health challenges and policy implications within Asia. It is designed for analysts, researchers, and policymakers interested in examining disease impacts over time and across different countries in the region. [Website](https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-yasin27mohammad/)

## Installation

You can install the development version of diseasesdeathrate from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-yasin27mohammad")
```

## Example

This basic example demonstrates how to calculate and visualize the average death rate from infectious and parasitic diseases for each Asian country in the dataset.

```{r ,example}
library(diseasesdeathrate)
library(ggplot2)
library(dplyr)


avg_death_rate <- infectious_parasitic_diseases_death_rate |>
  group_by(Entity) |>
  summarize(avg_death_rate = mean(`death rate per 100,000 population`, na.rm = TRUE))


ggplot(avg_death_rate, aes(x = reorder(Entity, -avg_death_rate), y = avg_death_rate, fill = avg_death_rate)) +
  geom_col() +
  scale_fill_gradient(low = "skyblue", high = "darkblue") +
  labs(
    title = "Average Death Rate from Infectious and Parasitic Diseases by Country (Asia)",
    x = "Country",
    y = "Average Death Rate per 100,000 Population"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, size = 8),
    plot.title = element_text(size = 10, face = "bold"),
    axis.title = element_text(size = 9.5),
    legend.position = "right"
  ) +
  guides(fill = guide_colorbar(title = "Avg Death Rate"))

```


## Overview of Key Functions in `diseasesdeathrate` package

The `diseasesdeathrate` package includes two essential functions that allow users to explore infectious and parasitic disease data across Asian countries:

- `avg_Deathrate()`: This function calculates the average death rate for infectious and parasitic diseases in a specified Asian country. By filtering the data for the selected country, it computes a single average value that reflects the overall impact of these diseases over time. This is useful for gaining a quick understanding of a country's long-term disease burden.

- `plot_death_rate_trend()`: This function generates a line plot that shows how death rates from infectious and parasitic diseases have changed over time for a particular Asian country. The trend line offers a clear visual of increases, decreases, or stability in death rates, helping users identify patterns and assess the effects of public health measures.
