---
title: "diseasesdeathrate Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{diseasesdeathrate Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```





The `diseasesdeathrate` package provides data and functions for exploring average death rates from infectious and parasitic diseases across Asian countries. The data covers a wide time span, specifically from 1950 to 2021, allowing for comprehensive analysis of trends and comparisons over time.

## Data Description

```{r, warning=FALSE, message=FALSE}
library(diseasesdeathrate)
library(ggplot2)
library(tibble)
library(dplyr)

```


```{r}
desc <- tibble(
  variable = c("Entity", "Code", "Year", "death rate per 100,000 population"),
  class = c("character", "character", "integer", "double"),
  description = c(
    "Country of record",
    "Country code",
    "Year of data collection",
    "Age-standardized death rate per 100,000 population"
  )
)

library(kableExtra)
kable(desc, caption = "Data Dictionary for `infectious_parasitic_diseases_death_rate` Dataset") %>%
  kable_styling(full_width = FALSE)

```


Below are descriptions of the primary functions included in the package:

- `avg_Deathrate()` - Calculates the average death rate of infectious and parasitic diseases for a specified country in Asia. This function filters data by country, calculates the mean of death rates, and returns the result. This function is useful for identifying long-term trends in death rates for particular countries.


## Data

```{r}
# Example of viewing the data structure
head(infectious_parasitic_diseases_death_rate)

```

## Example

### Using the `avg_Deathrate()` function

```{r}
avg_Deathrate("Japan")
```


